Discriminative Sensing Based on Signal Processing

### 2017-10-24 docs/thesis/chapters/appendix/b_pca_svm_cfa/pca_svm_cfa.tex
appendix configuration

\chapter{Critical Success Factor Analysis Based on Feaure Selection}
\label{ch:2_csf_fs}

\begin{quotation}[]{Paulo Freire}
No one knows it all. No one is ignorant of everything. We all know something. We are all ignorant of something.
\end{quotation}

@@

This chapter is organized as follows. In Section \ref{sec:ch2_relatedworks}, related works are discussed. Section \ref{sec:ch2_datamodel} presents the data model and the evaluated datasets. Section \ref{sec:ch2_csf_fs} describes the proposed approach for critical success factors analysis. Section \ref{sec:ch2_experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:ch2_conclusion} draws the conclusions.

\section{Related Works}
\label{sec:ch2_relatedworks}

@@

\section{Data Model}
\label{sec:ch2_datamodel}

@@

\section{An approach for Critical Success Factors Analysis}
\label{sec:ch2_csf_fs}

@@

\subsection{Visual Discriminant Analysis based on PCA}
\label{sec:ch2_pca}

@@

\subsection{CSF analysis based on RFE}
\label{sec:ch2_csfa}

@@

\section{Experiments and Results}
\label{sec:ch2_experimentalresults}

@@

\section{Conclusion}
\label{sec:ch2_conclusion}

>>>>

\chapter{Critical Success Factor Analysis Based on Feaure Selection}
\label{ch:b_csf_fs}

@@

This chapter is organized as follows. In Section \ref{sec:b_relatedworks}, related works are discussed. Section \ref{sec:b_datamodel} presents the data model and the evaluated datasets. Section \ref{sec:b_csf_fs} describes the proposed approach for critical success factors analysis. Section \ref{sec:b_experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:b_conclusion} draws the conclusions.

\section{Related Works}
\label{sec:b_relatedworks}

@@

\section{Data Model}
\label{sec:b_datamodel}

@@

\section{An approach for Critical Success Factors Analysis}
\label{sec:b_csf_fs}

@@

\subsection{Visual Discriminant Analysis based on PCA}
\label{sec:b_pca}

@@

\subsection{CSF analysis based on RFE}
\label{sec:b_csfa}

@@

\section{Experiments and Results}
\label{sec:b_experimentalresults}

@@

\section{Conclusion}
\label{sec:b_conclusion}
